### 2023-04-05 main.tex
i

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\usepackage{comment}
\usepackage{mathtools}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}

@@

	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}
where $S_{1}$ makes $H^{'}$ with both diagonal boundaries and $S_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\widetilde{\Psi}\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi\rangle$. The first transformation $S_{1}$ is closely related to the dual matrix. Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. This informally explains the role of duality. The second transformation $S_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs. \\
This idea is exposed as follows. We first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators. Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.

\begin{comment}
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\end{comment}
\subsubsection{The similarity transformation}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
\end{equation}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
\begin{equation}
    \mathcal{S}_{1}=S_{1}^{\otimes L}
\end{equation}
that is related with the duality matrix by 
\begin{equation}
\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
\end{equation}
 This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
\end{equation}
that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
\end{equation}
The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
\begin{equation}
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
\end{equation}
Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
The steady state $|\widehat{\Psi}\rangle$ of $H^{'}$ fulfils the equations
\begin{equation}
	H^{'}|\widehat{\Psi}\rangle=0
\end{equation}
therefore, it is easy to see that 
\begin{equation}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\widehat{\Psi}\rangle
\end{equation}

 We introduce the second transformation as 
 \begin{equation}
 	S_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}

@@

\subsubsection{The steady state of $\mathbb{H}$}\label{subsectionSSHsec}
We state the following result. The steady state of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 

@@

	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}|\mathbf{\bm{s}}\rangle

@@

To prove \eqref{ResulsBasis} we will consider the vector composed by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we will act on it with the similarity transformation \eqref{similarity} obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators than \eqref{bula} and simpler actions than \eqref{leftBoundary} and \eqref{rightBoundary}. This will allow to write explicitly the steady state \eqref{ResulsBasis}.

@@

We obtain the new operators of the MPA that by transforming the original one by \eqref{similarity} 

@@

Summing over $b\in \{1,\ldots,N\}$ in \eqref{bula} we have

@@

Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$ on the boundary vectors are given by 

@@

The vector $|\widetilde{\Psi}\rangle$ is written as:

@@

	|\widetilde{\Psi}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

We also observe that the vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\

@@

Fixing $ a\in \{2,\ldots,N\}$ and $\forall b,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{b}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{b-1}
	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{b-1}
	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}

@@

	\widetilde{X}_{1}^{b}\left(\widetilde{X}_{a}+b\lambda_{a}\right)^{n}

@@

To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$. Calling $\sum_{i=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have

@@

\subsubsection{The steady state of $\widehat{H}^{T}$}\label{subsectionSSdual}

@@

    |\widehat{\Psi}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\widehat{\Psi}(\bm{s})|\bm{s}\rangle 

@@

			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}

@@

\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{T}^{T}$ acts on the vector $|\widetilde{\Psi}\rangle$. The matrix $T^{T}$ is given by 
    T^{T}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}

@@

        T^{T}=\sum_{s_{1}=1}^{N}e_{i}^{x}+Q

@@

        	T^{T}\otimes T^{T}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)

@@

The matrix $T^{T}\otimes T^{T}$ has elements $\left\{\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2},q_{1},q_{2}\in \{1,\ldots,N\}}$, where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. We fix a raw of this matrix with arbitrary index $s_{1},s_{2}$
	\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
Iterating this tensor product for the chain of length $L$, we write the raw with indices $\bm{s}=s_{1},\ldots,s_{L}$
 of the matrix $\mathcal{T}^{T}$ as 
		\mathcal{T}^{T}_{\bm{s}}&=\left(T^{T}\right)^{\otimes L}_{s_{1},\ldots,s_{L}}=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{N}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}

@@

The product $\mathcal{T}^{T}|\widetilde{\Psi}\rangle$ gives a vector whose component are denoted by $\widehat{\Psi}(\bm{s})$ that are given by 

@@

		\widehat{\Psi}(\mathbf{s})&=\mathcal{T}^{T}_{\bm{s}}|\widetilde{\Psi}\rangle\\&= \widetilde{\Psi}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}

@@

	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
Because of the exponent $(1-\delta_{s_{x},1})$, the element $\widetilde{\Psi}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 

@@

		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\usepackage{comment}
\usepackage{mathtools}
\usepackage{array}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}

@@

	H\;\xrightarrow{\mathcal{S}_{1}}\;H^{'}\;\xrightarrow{\mathcal{S}_{2}}\;H^{''}
where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$. The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix. Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. This informally explains the role of duality. The second transformation $\mathcal{S}_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs. \\
This idea is exposed as follows. We first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators. Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.

\begin{comment}
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\end{comment}
\subsubsection{The similarity transformation}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
\end{equation}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
\begin{equation}
    \mathcal{S}_{1}=S_{1}^{\otimes L}
\end{equation}
that is related with the duality matrix by 
\begin{equation}
\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
\end{equation}
 This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
\end{equation}
that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
\end{equation}
The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
\begin{equation}
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
\end{equation}
Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
\begin{equation}
	H^{'}|\Psi^{'}\rangle=0
\end{equation}
therefore, it is easy to see that 
\begin{equation}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
\end{equation}

 We introduce the second transformation as 
 	S_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
By taking the tensor product over the chain we also define
	\mathcal{S}_{2}=S_{2}^{\otimes L}
Using $\mathcal{S}$ we introduce 
	H^{''}=B_{1}^{''}+H_{bulk}+B_{L}^{''}
that is similar to $H^{'}$ by $S_{2}$, i.e.
	H^{'}=\mathcal{S}_{2}^{-1}H^{''}\mathcal{S}_{2}
The boundary Hamiltonians are the following 
	B_{1}^{''}=e_{11}-\mathbbm{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}\qquad B_{L}^{''}=e_{11}-\mathbbm{1}
i.e. the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal. 
The steady state of $|\Psi^{''}\rangle$ of $H^{''}$ solves 
	H^{''}|\Psi^{''}\rangle=0
and it is related to $|\Psi^{'}\rangle$ by 
	|\Psi^{'}\rangle = \mathcal{S}_{2}^{-1}|\Psi^{''}\rangle
It is convenient to introduce also the similarity between $H$ and $H^{''}$, such that
H=\mathcal{S}^{-1}H^{''}\mathcal{S}
	S=S_{2}S_{1}=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}
	\mathcal{S}=S^{\otimes L}
This transformation connect the steady states of $H$ and $H^{''}$ by 
	|\Psi\rangle=\mathcal{S}^{-1}|\Psi^{''}\rangle
\begin{comment}

@@

\end{comment}
\subsubsection{The steady state of $J^{''}$}\label{subsectionSSHsec}
We state the following result. The steady state of the Hamiltonian $H^{''}$ is given by 

@@

	|\Psi^{''} \rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}|\mathbf{\bm{s}}\rangle

@@

To prove \eqref{ResulsBasis} we consider the vector with elements the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators. 

@@

We obtain the new operators of the MPA that by transforming the original one by $S$

@@

Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have

@@

Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{2,\ldots,N\}$ on the boundary vectors are given by 

@@

The vector $|\Psi^{''}\rangle$ is written as:

@@

	|Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

@@

Fixing $ a\in \{2,\ldots,N\}$ and for arbitrary $ \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{\ell-1}
	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}

@@

	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}

@@

To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$. Calling $\sum_{x=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have

@@

\subsubsection{The steady state of $H^{'}$}\label{subsectionSSdual}

@@

    |\Psi^{'}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi^{'}(\bm{s})|\bm{s}\rangle 

@@

			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}

@@

\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. The matrix $S_{2}^{-1}$, acting on a single site, is given by 
   S_{2}^{-1}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}

@@

        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{i}^{x}+Q

@@

        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)

@@

The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $s_{1},s_{2}$ reads
	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
We iterate this tensor product for the chain of length $L$, and we write the raw with indices arbitrary $\bm{s}=s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$ as
	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{N}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}

@@

The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$ that are given by 

@@

		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}

@@

\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 

@@

		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
